Dismal Code: Studying the Evolution of Security Bugs

### 2013-04-03 docs/evol.tex
minor fixes

We explored te relation between defects with the size of a project,
measured by the size of its jar file by carrying out correlation tests
between the size and the defect counts for each project and its
version. The results, all statistically significant ($p \ll
0.05$) can be seen in Table~\ref{tbl:jarsizecorr}. The {\it Security
  High} category stands out by having a remarkably lower effect than
the other categories, even {\it Security Low} that nearly tops the
list.

@@

To see whether bugs flock together we performed pairwise correlations
between all bug categories. We calculated the correlations between the
number of distinct bugs that appeared in a project throughout its
lifetime. The results can be seen in Table~\ref{tbl:corrmatrix} andsplncs.bst
Figure~\ref{fig:corrplot}. We found significant correlations between
all pairs apart from two pairs involving the {\it Security High}
category. In general, the {\it Security High} category showed the
weekest correlations with the other categories. Our results show that
in general bugs do flock together. We do not find projects with only a
certain kind of bug; bugs come upon projects in swarms of different
kinds. Bugs of the {\it Security High} category, though, are
different: they are either not associated with other bugs, or only
weakly so. Perhaps it takes a special kind of blunder to make it a
security hazard.

>>>>

We explored te relation between defects with the size of a project version,
measured by the size of its {\sc jar} file by carrying out correlation tests
between the size and the defect counts for each project and its
version. The results, all statistically significant ($p \ll
0.05$) can be seen in Table~\ref{tbl:jarsizecorr}. The {\it Security
  High} category stands out by having a remarkably lower effect than
the other categories, even {\it Security Low} that nearly tops the
list.

@@

To see whether bugs flock together we performed pairwise correlations
between all bug categories. We calculated the correlations between the
number of distinct bugs that appeared in a project throughout its
lifetime. The results can be seen in Table~\ref{tbl:corrmatrix} and
Figure~\ref{fig:corrplot}. We found significant correlations between
all pairs apart from two pairs involving the {\it Security High}
category. In general, the {\it Security High} category showed the
weekest correlations with the other categories. Our results show that
in general bugs do flock together. We do not find projects with only a
certain kind of bug; bugs come upon projects in swarms of different
kinds. Bugs of the {\it Security High} category, though, are
different: they are either not associated with other bugs, or only
weakly so. Perhaps it takes a special kind of blunder to make it a
security hazard.
